An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies

### 2017-05-17 main.tex
Authors TODO
Make amendments suggested by Marc.

@@

In this section the focus is on the ability of a mutant strategy to invade: the
probability of one individual of a given type successfully fixating in a
population of \(N - 1\) other individuals, denoted by \(x_1\).
The ranks of each strategy for all considered values of \(N\) according to mean
\(x_1\) are shown in Figures~\ref{fig_ranks_v_size_invade}.

@@

As well as noting that the memory length and complexity of these strategies are
much greater than one, it is interesting to note that none of them are akin to
memory one strategies. Only one is stochastic although close inspection of the
source code of PSO Gambler shows that it makes stochastic decisions rarely, and
is functionally very similar to its deterministic cousin Evolved Looker Up. Apart
from TF3 in \(N=3\), the finite state machines trained specifically for Moran
processes do not appear in the top 5 while strategies trained for tournaments do.
This is due to the nature of invasion: most of the opponents will initially be of
different types. The next section will consider the converse situation.

@@

>>>>

It is also noted that TF1, TF2 and TF3 all perform well. This is also the \(N\)
for which a zero determinant strategy does appear in the top 10\% ranking
strategies: ZD-extort-4. The performance of zero determinant strategies will be
examined more closely in Section~\ref{sec:population_size}.

@@

In this section the focus is on the ability of a mutant strategy to invade: the
probability of one individual of a given type successfully fixating in a
population of \(N - 1\) other individuals, denoted by \(x_1\).
The ranks of each strategy for all considered values of \(N\) according to mean
\(x_1\) are shown in Figure~\ref{fig:ranks_v_size_invade}.

@@

Only one of the above strategies is stochastic although close inspection of the
source code of PSO Gambler shows that it makes stochastic decisions rarely, and
is functionally very similar to its deterministic cousin Evolved Looker Up.
The PSO Gambler Mem1 strategy is a memory one strategy that has been trained to
maximise its utility and does perform well.
Apart from TF3, the finite state machines trained specifically for
Moran processes do not appear in the top 5, while strategies trained for
tournaments do. This is due to the nature of invasion: most of the opponents
will initially be different strategies. The next section will consider the
converse situation.

@@

% TODO: author contributions
